### 2014-06-17 ms/ms.Rmd
Added table with nr of observations by variable in ms.Rmd. Closes #114

library(plyr)
library(bibtex)
library(knitcitations)
source("MS-fun.R")
```

@@

>>>>

library(plyr)
library(bibtex)
library(knitcitations)
library(Hmisc)
# library(pander)

source("MS-fun.R")
```

@@

### C. Number of observations by variable

```{r echo=FALSE, message=FALSE}

thesevars <- setdiff(var.def$Variable[var.def$Type=="numeric"], 
                     c("map","mat","lai"))
Labels <- capitalize(var.def$label[var.def$Variable %in% thesevars])

Count <- function(x)length(data[[x]][!is.na(data[[x]])])
N <- sapply(thesevars, Count)

dfr <- data.frame(Variable=Labels, N=N)
dfr <- dfr[dfr$N > 0,]
rownames(dfr) <- NULL
```

```{r results='asis', echo=FALSE}
kable(dfr, "html", align="l")
```
